HPC--101 -- Cheatsheet \vspace{-2ex}

### 2016-01-22 hpc_101/cheatsheet/paper.tex
minor edit

\section{Miscellaneous}
\subsection{Commands}
\begin{itemize}
\item[] less \pth{file} \desc{Show contents of file\\Navigate using up/down arrow keys, spacebar, and pageup/pagedown keys\\  Press 'q' to exit out of less}
\item[] less -S \pth{file} \desc{Show contents of file without line wrap\\Navigate using up/down arrow keys, spacebar, and pageup/pagedown keys\\Press 'q' to exit out of less}

>>>>

\section{Miscellaneous}
\subsection{Commands}
\begin{itemize}
\item[] less \pth{file} \desc{Show contents of file\\Navigate using up/down arrow keys, spacebar, or pageup/pagedown keys\\  Press 'q' to exit out of less}
\item[] less -S \pth{file} \desc{Show contents of file without line wrap\\Navigate using up/down arrow keys, spacebar, or pageup/pagedown keys\\Press 'q' to exit out of less}
